Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-25 products/manuscript/Manuscript.qmd
img

---
title: "Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting"
author: ""
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r fig-table1, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table1Baseline.png")

@@

```{r,echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics("Images/Table4Interaction.png")
```

@@

```{r fig-adjusted-u25, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  normalizePath(
    here::here("Images", "AdjustedRatio.png"),
    winslash = "/"
  )
)

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  normalizePath(
    here::here("Images", "Figure 3. Predicted Probability.png"),
    winslash = "/"
  )
)

@@

**Figure 4 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Build an absolute, forward‐slash path and then include the graphic
fig4_path <- normalizePath(
  here::here(
    "Images",
    "Figure 4.Comparative Discriminative Performance of ML .png"
  ),
  winslash = "/"
)

knitr::include_graphics(fig4_path)

@@

**Table 6:  Discriminative Performance (AUC) of Machine Learning Models Predicting Adverse Birth Outcomes Under Different IPTp Regimens**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(here::here("Images", "Table6.Discriminative Performance (AUC) of ML Models.png"))

>>>>

---
title: "Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting"
author: ""
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
resources:
  - Images/**
execute:
  root: .
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

@@

```{r fig-table1, echo=FALSE, message=FALSE, warning=FALSE}
# 2) Build the absolute, Pandoc-friendly path
table1_path <- normalizePath(
  here::here("products", "manuscript", "Images", "Table1Baseline.png"),
  winslash = "/"
)

# 3) Embed the image
knitr::include_graphics(table1_path)
```

@@

```{r,echo=FALSE, message=FALSE, warning=FALSE}
# 2) Build the absolute, Pandoc-friendly path to Table4Interaction.png
table4_path <- normalizePath(
  here::here("products", "manuscript", "Images", "Table4Interaction.png"),
  winslash = "/"
)

# 3) Embed the image
knitr::include_graphics(table4_path)
```

@@

```{r fig-adjusted-u25, echo=FALSE, message=FALSE, warning=FALSE}
# 2) Build a forward-slash absolute path to the image
adjusted_path <- normalizePath(
  here::here("products", "manuscript", "Images", "AdjustedRatio.png"),
  winslash = "/"
)

# 3) Embed the image
knitr::include_graphics(adjusted_path)
```

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# 2) Build the absolute, Pandoc-friendly path to Figure 3
fig3_path <- normalizePath(
  here::here(
    "products", "manuscript", "Images",
    "Figure 3. Predicted Probability.png"
  ),
  winslash = "/"
)

# 3) Embed the image
knitr::include_graphics(fig3_path)
```

@@

**Figure 4 : Comparative Discriminative Performance of ML Models for Predicting Adverse Birth Outcomes**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# 2) Build the absolute, Pandoc-friendly path to Figure 4
fig4_path <- normalizePath(
  here::here(
    "products", "manuscript", "Images",
    "Figure 4.Comparative Discriminative Performance of ML .png"
  ),
  winslash = "/"
)

# 3) Embed the image
knitr::include_graphics(fig4_path)
```

@@

**Table 6:  Discriminative Performance (AUC) of Machine Learning Models Predicting Adverse Birth Outcomes Under Different IPTp Regimens**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# 2) Build the absolute, Pandoc‐friendly path to Table 6
table6_path <- normalizePath(
  here::here(
    "products", "manuscript", "Images",
    "Table6.Discriminative Performance (AUC) of ML Models.png"
  ),
  winslash = "/"
)

# 3) Embed the image
knitr::include_graphics(table6_path)
```
